Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-12-28 paper/paper.tex
made minor changes to results paragraph that I think clean up the concepts without overstating. Changed cycloheximide sentence a little in supplement to point out its issue with regards to IFN a bit more bluntly and added another citation

The single-cell data also suggest heterogeneity in the process by which different viral variants induce IFN.
Specifically, these data show that NS-deficient virions are much more likely to induce IFN when they transcribe more RNA, but that there is no such association for other virions (\FIG{mutations}D).
To validate this conclusion, we used flow cytometry to compare IFN induction among cells that express low or high levels of the viral HA protein under the assumption that protein levels correlate with viral transcription.
Consistent with the single-cell data, the NS1stop or NS1-A122V viruses are much more likely to induce IFN if they express high levels of HA (\FIG{mutantcomparison}A and \SUPPFIG{mutantcomparison_supp}A).
In contrast, wild-type or PB1-mutant viruses are only slightly more likely to induce IFN if they express more HA. 
To confirm that higher viral transcription or genome replication \emph{cause} more IFN induction by NS-deficient virions, we treated infected cells with chemicals (ribavirin or cycloheximide) that inhibit secondary viral transcription~\citep{Vanderlinden:2016ec,reuther2015generation,Scholtissek:1976wg, killip2014activation}.
Both inhibitors strongly reduced IFN induction by cells infected with NS1stop virus, but not cells infected by virus with a deletion in PB1 (\FIG{mutantcomparison}B and \SUPPFIG{mutantcomparison_supp}B).
Therefore, different viral variants induce IFN by different processes.

@@

\caption{
{\bf Additional data for comparison of IFN induction as a function of viral load, related to \FIG{mutantcomparison}.}
{\bf (A)}
Detailed analysis of the relationship among HA expression and IFN induction for different viral mutants that is summarized in \FIG{mutantcomparison}A.
We re-analyzed all the infected cells in \SUPPFIG{validation_supp}A (defining ``infected'' using the same HA-gating scheme in \SUPPFIG{validation_supp}A) for the wild-type virus, the NS1stop virus, and the three amino-acid mutants with significantly increased IFN induction.
For each virus and replicate, we binned the infected cells into HA expression quartiles.
We then calculated the percent of cells that were IFN+ in each quartile (defining ``IFN+'' using the same gating scheme in \SUPPFIG{validation_supp}A).
The plots show the mean HA expression in each quartile versus the percent of cells that are IFN+.
The results clearly indicate that for the NS1stop virus, increased viral burden (more HA) correlates with IFN induction.
A similar trend also holds for the virus with an amino-acid substitution in NS1 (NS1-A122V). 
But for wild type and the two PB1 mutants, there is no clear trend for higher viral burden to correlate with IFN induction.
\FIG{mutantcomparison}A summarizes the data in this figure by simply showing the ratio of the percent IFN+ of the highest HA-expression quartile to the lowest HA-expression quartile for each sample and replicate.
{\bf (B)}
Similar to \FIG{mutantcomparison}B, but uses cycloheximide rather than ribavirin.
Preventing viral secondary transcription using cycloheximide also decreases IFN induction by the NS1stop virus relative to the PB1 deletion virus, corroborating the result in \FIG{mutantcomparison}B with a different inhibitor.
However, the results are more complex here, since cycloheximide alone increases IFN production~\citep{raj1981analysis, maroteaux1983cycloheximide, killip2014activation}.
Therefore, we see an increase in IFN levels upon cycloheximide treatment for uninfected cells and cells infected with the PB1 deletion virus, but a decrease for cells infected with the NS1stop virus.
This plot shows qPCR results for the same samples as in \SUPPFIG{validation_supp}C, but with the qPCR for expression of IFNB1 transcripts relative to the housekeeping gene L32.
As described in \SUPPFIG{validation_supp}C, A549 cells were infected at an MOI of 0.4, such that HA expression was equivalent between viral variants when secondary transcription was blocked, and some of the samples treated with 50 $\mu$g/ml of cycloheximide~\citep[a concentration sufficient to block secondary transcription;][]{killip2014activation}.
After 8 hours, transcript levels were quantified by qPCR.
Points indicate four replicates, and lines indicate the mean.
The dashed line shows the limit of detection, and points below this limit where set to that value.
}
\label{suppfig:mutantcomparison_supp}
\end{suppfig}

>>>>

The single-cell data also suggest heterogeneity in the process by which different viral variants induce IFN.
Specifically, these data show that NS-deficient virions are much more likely to induce IFN when they transcribe more RNA, but that there is no such association for other virions (\FIG{mutations}D).
To validate this conclusion, we used flow cytometry to compare IFN induction among cells that express low or high levels of the viral HA protein under the assumption that protein levels correlate with viral transcription.
Consistent with the single-cell data, the NS1stop or NS1-A122V viruses are much more likely to induce IFN if they express high levels of HA (\FIG{mutantcomparison}A and \SUPPFIG{mutantcomparison_supp}A).
In contrast, wild-type or PB1-mutant viruses are only slightly more likely to induce IFN if they express more HA. 
To confirm that higher viral transcription or genome replication \emph{drive} IFN induction by NS-deficient virions, we treated infected cells with either ribavirin or cycloheximide, inhibiting secondary viral transcription~\citep{Vanderlinden:2016ec,reuther2015generation,Scholtissek:1976wg, killip2014activation}.
Both inhibitors strongly reduced IFN induction by cells infected with NS1stop virus, but not cells infected by virus with a deletion in PB1---a virus for which induction of interferon could not be dependent on secondary viral transcription or replication due to its fundamental inability to engage in these processes (\FIG{mutantcomparison}B and \SUPPFIG{mutantcomparison_supp}B).
These data support a more complex model of interferon induction by influenza, wherein different viral variants trigger the production of IFN by different processes.

@@

\caption{
{\bf Additional data for comparison of IFN induction as a function of viral load, related to \FIG{mutantcomparison}.}
{\bf (A)}
Detailed analysis of the relationship among HA expression and IFN induction for different viral mutants that is summarized in \FIG{mutantcomparison}A.
We re-analyzed all the infected cells in \SUPPFIG{validation_supp}A (defining ``infected'' using the same HA-gating scheme in \SUPPFIG{validation_supp}A) for the wild-type virus, the NS1stop virus, and the three amino-acid mutants with significantly increased IFN induction.
For each virus and replicate, we binned the infected cells into HA expression quartiles.
We then calculated the percent of cells that were IFN+ in each quartile (defining ``IFN+'' using the same gating scheme in \SUPPFIG{validation_supp}A).
The plots show the mean HA expression in each quartile versus the percent of cells that are IFN+.
The results clearly indicate that for the NS1stop virus, increased viral burden (more HA) correlates with IFN induction.
A similar trend also holds for the virus with an amino-acid substitution in NS1 (NS1-A122V). 
But for wild type and the two PB1 mutants, there is no clear trend for higher viral burden to correlate with IFN induction.
\FIG{mutantcomparison}A summarizes the data in this figure by simply showing the ratio of the percent IFN+ of the highest HA-expression quartile to the lowest HA-expression quartile for each sample and replicate.
{\bf (B)}
Similar to \FIG{mutantcomparison}B, but uses cycloheximide rather than ribavirin.
Preventing viral secondary transcription using cycloheximide also decreases IFN induction by the NS1stop virus relative to the PB1 deletion virus, corroborating the result in \FIG{mutantcomparison}B with a different inhibitor.
However, the results are more complex here, since cycloheximide alone increases IFN production, even in response to non-viral challenges such as poly I:C ~\citep{raj1981analysis, maroteaux1983cycloheximide, ringold1984cycloheximide, killip2014activation}.
Therefore, we see an increase in IFN levels upon cycloheximide treatment for uninfected cells and cells infected with the PB1 deletion virus, but a decrease for cells infected with the NS1stop virus.
This plot shows qPCR results for the same samples as in \SUPPFIG{validation_supp}C, but with the qPCR for expression of IFNB1 transcripts relative to the housekeeping gene L32.
As described in \SUPPFIG{validation_supp}C, A549 cells were infected at an MOI of 0.4, such that HA expression was equivalent between viral variants when secondary transcription was blocked, and some of the samples treated with 50 $\mu$g/ml of cycloheximide~\citep[a concentration sufficient to block secondary transcription;][]{killip2014activation}.
After 8 hours, transcript levels were quantified by qPCR.
Points indicate four replicates, and lines indicate the mean.
The dashed line shows the limit of detection, and points below this limit where set to that value.
}
\label{suppfig:mutantcomparison_supp}
\end{suppfig}
